Exploring the conformational dynamics of a large molecule in solution using an external electric field: A nonequilibrium molecular dynamics simulation

### 2013-11-04 writedown/npt-neq/alanine.tex
backup ..

\title{Exploring the conformational dynamics of a large molecule in solution using an external electric field: A Nonequilibrium Molecular Dynamics Simulation}
% \title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Christof Sch\"utte}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\affiliation{Zuse Institute Berlin, Germany}
\author{Giovanni Ciccotti}
\affiliation{Department of Physics, University of Roma "La Sapienza", Italy}
\author{Luigi Delle Site}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}

\begin{abstract}
  In this paper, we investigate the conformational dynamics of alanine
  dipeptide under an external electric field (EF) by the
  nonequilibrium molecular dynamics (MD) simulation, which enables us
  to calculate the nonequilibrium physical properties that are not
  available for traditional equilibrium MD simulation.  We study both
  the constant and oscillatory EF cases, and discuss the way to
  implement the temperature control in the nonequilibrium MD
  simulation, which removes the irrelevant thermal effect of the EF
  from the system. In the constant EF case, different time-scales are
  discovered in the conformational, dipole moment, and orientational
  dynamics. Moreover, we prove that the solvent structure only
  marginally changes when the external EF is switched on.  In the
  oscillatory EF case, the conformational changes are shown to be as
  strong as constant EF case, and non-trivial nonequilibrium
  conformational circulations are presented by calculating the
  integrated net probability fluxes.
\end{abstract}

>>>>

\title{Exploring the conformational dynamics of a large molecule in solution using an external electric field: A nonequilibrium molecular dynamics simulation}
% \title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Christof Sch\"utte}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\affiliation{Zuse Institute Berlin, Germany}
\author{Giovanni Ciccotti}
\affiliation{Department of Physics, University of Roma "La Sapienza", Italy}
\author{Luigi Delle Site}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}

\begin{abstract}
In this paper, we investigate the conformational dynamics of alanine
   dipeptide under an external electric field by the
   nonequilibrium molecular dynamics simulation.  We consider
   the case of a constant and of an oscillatory field. In this context we
propose a procedure to
   implement the temperature control, which removes the irrelevant thermal
effects of the field. For the constant field different time-scales are
   identified  in the conformational, dipole moment, and orientational
   dynamics. Moreover, we prove that the solvent structure only
   marginally changes when the external field is switched on.  In the
   case of oscillatory field, the conformational changes are shown to be as
   strong as the previous case, and non-trivial nonequilibrium
   circular paths in the conformation space are revealed by calculating the
   integrated net probability fluxes.
  % In this paper, we investigate the conformational dynamics of alanine
  % dipeptide under an external electric field (EF) by the
  % nonequilibrium molecular dynamics (MD) simulation, which enables us
  % to calculate the nonequilibrium physical properties that are not
  % available for traditional equilibrium MD simulation.  We study both
  % the constant and oscillatory EF cases, and discuss the way to
  % implement the temperature control in the nonequilibrium MD
  % simulation, which removes the irrelevant thermal effect of the EF
  % from the system. In the constant EF case, different time-scales are
  % discovered in the conformational, dipole moment, and orientational
  % dynamics. Moreover, we prove that the solvent structure only
  % marginally changes when the external EF is switched on.  In the
  % oscillatory EF case, the conformational changes are shown to be as
  % strong as constant EF case, and non-trivial nonequilibrium
  % conformational circulations are presented by calculating the
  % integrated net probability fluxes.
\end{abstract}
